Manuscript 1: Adult Health Effects

### 2021-02-02 paperone_adult_health.Rmd
Changes to meet reviewer comments for JUH.

library(tidyverse)
library(gridExtra)
library(RColorBrewer)
library(tableone)
library(latex2exp)
library(labelled)
library(kableExtra)
library(tigris)
library(sf)
library(spdep)
library(logistf)

@@

@@

var_label(mydata$collapseeduc) <- "Education level"
var_label(mydata$public_benefits) <- "Receives public benefits"
var_label(mydata$collapsemarital) <- "Marital status"
var_label(mydata$num_time_notice) <- "How long after water switch to notice water issue? (months)"
var_label(mydata$blood_test_after_april_2014) <- "Received blood lead test"
var_label(mydata$elevated_lead_after_april_2014) <- "Had elevated lead"
var_label(mydata$rashes_after_april_2014) <- "Had rashes"
var_label(mydata$hairloss_after_april_2014) <- "Had hair loss"
var_label(mydata$nausea_after_april_2014) <- "Had nausea"
var_label(mydata$irritable_after_april_2014) <- "Was irritable"
var_label(mydata$ptsd_bin) <- "PTSD"
var_label(mydata$phq_bin) <- "Depression/Anxiety"

mydata_complete <- filter(mydata, !is.na(age), !is.na(reth), !is.na(marital_status), !is.na(educ_level), !is.na(public_benefits), !is.na(gender), !is.na(confidants2), !is.na(years_cityflint), !is.na(current_zip), !is.na(blood_test_after_april_2014), !is.na(blood_test_before_april_2014), !is.na(elevated_lead_before_april_2014), !is.na(elevated_lead_after_april_2014), !is.na(rashes_before_april_2014), !is.na(rashes_after_april_2014), !is.na(hairloss_before_april_2014), !is.na(hairloss_after_april_2014), !is.na(nausea_before_april_2014), !is.na(nausea_after_april_2014), !is.na(irritable_before_april_2014), !is.na(irritable_after_april_2014), !is.na(ptsdscore), !is.na(phq), gender != "Transgender Woman", !is.na(num_time_notice))
```

We assemble some descriptives and maps on the complete data:
```{r, echo=TRUE, message=FALSE, warning=FALSE}
zcta1 <- zctas(cb = TRUE, starts_with = c("4850", "48532"), class = "sf") %>% filter(ZCTA5CE10 != "48509")
flintdat <- data.frame("zip" = zcta1$ZCTA5CE10, "geometry" = zcta1$geometry)

@@

flintdat2 <- full_join(flintdat, totalpop, by=c("zip" = "current_zip"))

popmap <- ggplot(data=flintdat2) + geom_sf(data=flintdat2, aes(geometry = geometry, fill = factor(pop)), size=0, alpha = 0.6) + geom_sf(data=flint_boundary, aes(geometry=geometry), fill=NA, color = "black") + geom_sf_label(aes(geometry = geometry, label = paste0(zip, " (", pop, ")"))) + xlab(" ") + ylab(" ") + theme(rect = element_blank(), axis.ticks = element_blank(), axis.line=element_blank(),axis.text.x=element_blank(), axis.text.y=element_blank(), legend.position = "none") + scale_fill_grey()

@@

ggsave(filename = "mymap.pdf", plot = popmap, width = 8, height = 8)

var_label(mydata_complete$collapseeduc) <- "Education level"
var_label(mydata_complete$public_benefits) <- "Receives public benefits"
var_label(mydata_complete$collapsemarital) <- "Marital status"
var_label(mydata_complete$num_time_notice) <- "How long after water switch to notice water issue? (months)"
var_label(mydata_complete$blood_test_after_april_2014) <- "Received blood lead test"
var_label(mydata_complete$elevated_lead_after_april_2014) <- "Had elevated lead"
var_label(mydata_complete$rashes_after_april_2014) <- "Had rashes"
var_label(mydata_complete$hairloss_after_april_2014) <- "Had hair loss"
var_label(mydata_complete$nausea_after_april_2014) <- "Had nausea"
var_label(mydata_complete$irritable_after_april_2014) <- "Was irritable"
var_label(mydata_complete$ptsd_bin) <- "PTSD"
var_label(mydata_complete$phq_bin) <- "Depression/Anxiety"

table_missing <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2", "num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), strata = "include", data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))

table_predictors <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), strata = "collapserace", data=mydata, includeNA = TRUE, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))

kable(print(table_predictors, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(5:9, 11:13, 15:17)) %>% kable_styling(position="center")

kable(print(table_outcomes, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:6, 8:10, 12:14, 16:18, 20:22, 24:26)) %>% kable_styling(position="center")

table_predictors_notstrat <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA=TRUE)

kable(print(table_missing, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:6, 8:12, 14:16, 18:20, 26:28, 30:32, 34:36, 38:40, 42:44)) %>% kable_styling(position="center")

test <- print(table_missing, contDigits=1, varLabel = T, printToggle=FALSE)

kable(print(table_predictors_notstrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(5:9, 11:13, 15:17)) %>% kable_styling(position="center")

kable(print(table_outcomes_notstrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:6, 8:10, 12:14, 16:18, 20:22, 24:26)) %>% kable_styling(position="center")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("~/Desktop/Research/Jerel Flint/Analyses/sample_inclusion.png")
```

@@

As we know, when trying to understand the effect of a mediated effect on some outcome, we DO NOT adjust for the mediator. However, when trying to understand the effect of the mediator on the outcome, we DO adjust for the mediated effect. Therefore, we have to fit several models for our different outcomes, adjusting for different things depending on what the predictor of interest is. All told, we consider 10 different outcomes (PTSD, PHQ, rashes, hair loss, nausea, irritability, overall number of symptoms, elevated blood lead, getting tested, time to noticing issues) and consider the classes of predictors: demographics/baseline, time to noticing issues/getting tested, elevated blood lead, and emergence of symptoms. This results in us fitting 17 different models, given here:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
mydata_complete$collapsezip <- ifelse(mydata_complete$current_zip==48502, 2, mydata_complete$current_zip)
mydata_complete$collapsezip <- factor(mydata_complete$collapsezip, levels=c(2:7), labels=c("48502/48503", "48504", "48505", "48506", "48507", "48532"))
mydata_complete$collapsepubben <- ifelse(mydata_complete$public_benefits=="Yes", "Yes", "No")

ptsd_dem <- glm(ptsd_bin ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="binomial")

summary(ptsd_dem)

phq_dem <- glm(phq_bin ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="binomial")

summary(phq_dem)

rash_dem <- glm(rash_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="binomial")

summary(rash_dem)

hairloss_dem <- glm(hair_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="binomial")

summary(hairloss_dem)

nausea_dem <- glm(nausea_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="binomial")

summary(nausea_dem)

irritable_dem <- glm(irritable_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="binomial")

summary(irritable_dem)

overall_dem <- glm(overall_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="poisson")

summary(overall_dem)

bloodlead_dem <- logistf(elevated_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data = mydata_complete)

test1 <- summary(bloodlead_dem)

gettest_dem <- glm(bloodtest_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="binomial")

summary(gettest_dem)

time_dem <- lm(log(num_time_notice) ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete)

summary(time_dem)

mydata_complete$rash_collapse_before <- ifelse(mydata_complete$rashes_before_april_2014=="Yes", "Yes", "No")
mydata_complete$hair_collapse_before <- ifelse(mydata_complete$hairloss_before_april_2014=="Yes", "Yes", "No")
mydata_complete$nausea_collapse_before <- ifelse(mydata_complete$nausea_before_april_2014=="Yes", "Yes", "No")
mydata_complete$irritable_collapse_before <- ifelse(mydata_complete$irritable_before_april_2014=="Yes", "Yes", "No")
mydata_complete$bloodtest_collapse_before <- ifelse(mydata_complete$blood_test_before_april_2014=="Yes", "Yes", "No")

ptsd_symp <- glm(ptsd_bin ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip + overall_collapse + elevated_collapse + bloodtest_collapse + num_time_notice, data=mydata_complete, family="binomial")

summary(ptsd_symp)

phq_symp <- glm(phq_bin ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip + overall_collapse + elevated_collapse + bloodtest_collapse + num_time_notice, data=mydata_complete, family="binomial")

summary(phq_symp)

rash_symp <- logistf(rash_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip + hair_collapse + nausea_collapse + irritable_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + rash_collapse_before, data=mydata_complete)

test2 <- summary(rash_symp)

hairloss_symp <- logistf(hair_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip + rash_collapse + nausea_collapse + irritable_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + hair_collapse_before, data=mydata_complete)

test3 <- summary(hairloss_symp)

nausea_symp <- logistf(nausea_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip + rash_collapse + hair_collapse + irritable_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + nausea_collapse_before, data=mydata_complete)

test4 <- summary(nausea_symp)

irritable_symp <- logistf(irritable_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip + rash_collapse + hair_collapse + nausea_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + irritable_collapse_before, data=mydata_complete)

test5 <- summary(irritable_symp)

overall_bloodlead <- glm(overall_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip + elevated_collapse + bloodtest_collapse + num_time_notice + rash_collapse_before + hair_collapse_before + nausea_collapse_before + irritable_collapse_before, data=mydata_complete, family="poisson")

summary(overall_bloodlead)
```

Since we fit quite a few models, we use the FDR to adjust for our multiple testing.
```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Assembling a data frame of desired coefficients, confidence intervals, and p-values:
myresults <- data.frame("Outcome" = c(rep("PTSD", length(summary(ptsd_dem)$coefficients[-1,1])), rep("PHQ", length(summary(phq_dem)$coefficients[-1,1])), rep("Rashes", length(summary(rash_dem)$coefficients[-1,1])), rep("Hairloss", length(summary(hairloss_dem)$coefficients[-1,1])), rep("Nausea", length(summary(nausea_dem)$coefficients[-1,1])), rep("Irritable", length(summary(irritable_dem)$coefficients[-1,1])), rep("Overall", length(summary(overall_dem)$coefficients[-1,1])), rep("Elevated lead", length(test1$coefficients[-1])), rep("Get tested", length(summary(gettest_dem)$coefficients[-1,1])), rep("Time to notice", length(summary(time_dem)$coefficients[-1,1])), rep("PTSD", length(summary(ptsd_symp)$coefficients[15:18,1])), rep("PHQ", length(summary(phq_symp)$coefficients[15:18,1])), rep("Rashes", length(test2$coefficients[15:20])), rep("Hairloss", length(test3$coefficients[15:20])), rep("Nausea", length(test4$coefficients[15:20])), rep("Irritable", length(test5$coefficients[15:20])), rep("Overall", length(summary(overall_bloodlead)$coefficients[15:17,1]))))

myresults$Predictor <- c(rownames(summary(ptsd_dem)$coefficients[-1,]), rownames(summary(phq_dem)$coefficients[-1,]), rownames(summary(rash_dem)$coefficients[-1,]), rownames(summary(hairloss_dem)$coefficients[-1,]), rownames(summary(nausea_dem)$coefficients[-1,]), rownames(summary(irritable_dem)$coefficients[-1,]), rownames(summary(overall_dem)$coefficients[-1,]), names(test1$coefficients[-1]), rownames(summary(gettest_dem)$coefficients[-1,]), rownames(summary(time_dem)$coefficients[-1,]), rownames(summary(ptsd_symp)$coefficients[15:18,]), rownames(summary(phq_symp)$coefficients[15:18,]), names(test2$coefficients[15:20]), names(test3$coefficients[15:20]), names(test4$coefficients[15:20]), names(test5$coefficients[15:20]), rownames(summary(overall_bloodlead)$coefficients[15:17,]))

myresults$Coefficient <- c(summary(ptsd_dem)$coefficients[-1,1], summary(phq_dem)$coefficients[-1,1], summary(rash_dem)$coefficients[-1,1], summary(hairloss_dem)$coefficients[-1,1], summary(nausea_dem)$coefficients[-1,1], summary(irritable_dem)$coefficients[-1,1], summary(overall_dem)$coefficients[-1,1], test1$coefficients[-1], summary(gettest_dem)$coefficients[-1,1], summary(time_dem)$coefficients[-1,1], summary(ptsd_symp)$coefficients[15:18,1], summary(phq_symp)$coefficients[15:18,1], test2$coefficients[15:20], test3$coefficients[15:20], test4$coefficients[15:20], test5$coefficients[15:20], summary(overall_bloodlead)$coefficients[15:17,1])

>>>>

library(tidyverse)
library(gridExtra)
library(RColorBrewer)
library(tableone)
library(latex2exp)
library(labelled)
library(kableExtra)
library(tigris)
library(sf)
library(spdep)
library(logistf)
library(mice)

@@

mydata$phq <- rowSums(select(mydata, nervousscore, depressedscore, nopleasurescore, worryscore), na.rm=TRUE)
mydata$phq[is.na(mydata$nervousscore)] <- NA_real_

@@

mydata$employ_collapse <- case_when(
  mydata$employ_status=="Jobs/sporadic" | mydata$employ_status=="Other" ~ "Other",
  mydata$employ_status=="Retired" ~ "Retired",
  mydata$employ_status=="Employed" ~ "Employed",
  mydata$employ_status=="Unemployed" ~ "Unemployed",
  is.na(mydata$employ_status) ~ NA_character_)

var_label(mydata$collapseeduc) <- "Education level"
var_label(mydata$public_benefits) <- "Receives public benefits"
var_label(mydata$collapsemarital) <- "Marital status"
var_label(mydata$num_time_notice) <- "How long after water switch to notice water issue? (months)"
var_label(mydata$blood_test_after_april_2014) <- "Received blood lead test"
var_label(mydata$elevated_lead_after_april_2014) <- "Had elevated lead"
var_label(mydata$rashes_after_april_2014) <- "Had rashes"
var_label(mydata$hairloss_after_april_2014) <- "Had hair loss"
var_label(mydata$nausea_after_april_2014) <- "Had nausea"
var_label(mydata$irritable_after_april_2014) <- "Was irritable"
var_label(mydata$ptsd_bin) <- "PTSD"
var_label(mydata$phq_bin) <- "Depression/Anxiety"
var_label(mydata$employ_collapse) <- "Employment status"

mydata_complete <- filter(mydata, !is.na(age), !is.na(reth), !is.na(marital_status), !is.na(educ_level), !is.na(public_benefits), !is.na(gender), !is.na(confidants2), !is.na(years_cityflint), !is.na(current_zip), !is.na(blood_test_after_april_2014), !is.na(blood_test_before_april_2014), !is.na(elevated_lead_before_april_2014), !is.na(elevated_lead_after_april_2014), !is.na(rashes_before_april_2014), !is.na(rashes_after_april_2014), !is.na(hairloss_before_april_2014), !is.na(hairloss_after_april_2014), !is.na(nausea_before_april_2014), !is.na(nausea_after_april_2014), !is.na(irritable_before_april_2014), !is.na(irritable_after_april_2014), !is.na(ptsdscore), !is.na(phq), gender != "Transgender Woman", !is.na(num_time_notice), !is.na(employ_collapse))
```

We assemble some descriptives on the data:
```{r, echo=TRUE, message=FALSE, warning=FALSE}
table_predictors <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "employ_collapse", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), strata = "collapserace", data=mydata, includeNA = TRUE, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))

kable(print(table_predictors, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:6, 8:12, 14:18, 20:22, 24:26)) %>% kable_styling(position="center")

kable(print(table_outcomes, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:7, 9:12, 14:17, 19:22, 24:27, 29:32, 36:38)) %>% kable_styling(position="center")

table_predictors_notstrat <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "employ_collapse", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA=TRUE)

kable(print(table_predictors_notstrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:6, 8:12, 14:18, 20:22, 24:26)) %>% kable_styling(position="center")

kable(print(table_outcomes_notstrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:7, 9:12, 14:17, 19:22, 24:27, 29:32, 36:38)) %>% kable_styling(position="center")
```

We make maps and descriptive statistics:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
zcta1 <- zctas(cb = TRUE, starts_with = c("4850", "48532"), class = "sf") %>% filter(ZCTA5CE10 != "48509")
flintdat <- data.frame("zip" = zcta1$ZCTA5CE10, "geometry" = zcta1$geometry)

@@

flintdat2 <- full_join(flintdat, totalpop, by=c("zip" = "current_zip")) 
sites <- read_csv("survey_locations.csv")

popmap <- ggplot(data=flintdat2) + geom_sf(data=flintdat2, aes(geometry = geometry, fill = factor(pop)), size=0, alpha = 0.6) + geom_sf(data=flint_boundary, aes(geometry=geometry), fill=NA, color = "black") + geom_sf_label(aes(geometry = geometry, label = paste0(zip, " (", pop, ")"))) + xlab(" ") + ylab(" ") + theme(rect = element_blank(), axis.ticks = element_blank(), axis.line=element_blank(), axis.text.x=element_blank(), axis.text.y=element_blank(), legend.position = "none") + scale_fill_grey() + geom_point(data = sites, aes(x = Longitude, y = Latitude), color = "red", shape = 8)

@@

ggsave(filename = "~/Desktop/Research/Jerel Flint/Publications/Paper 1 - Adult Health/mymap.pdf", plot = popmap, width = 8, height = 8)

#table_predictors <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), strata = "collapserace", data=mydata, includeNA = TRUE, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))

#table_outcomes <- CreateTableOne(vars=c("num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), strata = "collapserace", data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)

#kable(print(table_predictors, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:6, 8:12, 14:16, 18:20)) %>% kable_styling(position="center")

#kable(print(table_outcomes, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:7, 9:12, 14:17, 19:22, 24:27, 29:32, 36:38)) %>% kable_styling(position="center")

#table_predictors_notstrat <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA=TRUE)

#table_outcomes_notstrat <- CreateTableOne(vars=c("num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA=TRUE)

#kable(print(table_predictors_notstrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:6, 8:12, 14:16, 18:20)) %>% kable_styling(position="center")

#kable(print(table_outcomes_notstrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:7, 9:12, 14:17, 19:22, 24:27, 29:32, 36:38)) %>% kable_styling(position="center")
```

@@

Per reviewer request, we use multiple imputation with chained equations to impute missingness in the dataset:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
mydata$collapsezip <- ifelse(mydata$current_zip==48502, 2, mydata$current_zip)
mydata$collapsezip <- factor(mydata$collapsezip, levels=c(2:7), labels=c("48502/48503", "48504", "48505", "48506", "48507", "48532"))
mydata$collapsepubben <- ifelse(mydata$public_benefits=="Yes", "Yes", "No")
mydata$collapsegender <- ifelse(mydata$gender=="Transgender Woman", "Female", mydata$gender)
mydata$rash_collapse_before <- ifelse(mydata$rashes_before_april_2014=="Yes", 1, 0)
mydata$hair_collapse_before <- ifelse(mydata$hairloss_before_april_2014=="Yes", 1, 0)
mydata$nausea_collapse_before <- ifelse(mydata$nausea_before_april_2014=="Yes", 1, 0)
mydata$irritable_collapse_before <- ifelse(mydata$irritable_before_april_2014=="Yes", 1, 0)
mydata$bloodtest_collapse_before <- ifelse(mydata$blood_test_before_april_2014=="Yes", 1, 0)

mydata_complete <- select(mydata, age, collapsegender, collapserace, collapsepubben, collapseeduc, employ_collapse, number_children, years_cityflint, confidants2, collapsezip, ptsd_bin, phq_bin, rash_collapse, hair_collapse, nausea_collapse, irritable_collapse, overall_collapse, elevated_collapse, bloodtest_collapse, num_time_notice, rash_collapse_before, hair_collapse_before, nausea_collapse_before, irritable_collapse_before, bloodtest_collapse_before)

mydata_complete$collapsegender <- factor(mydata_complete$collapsegender)
mydata_complete$collapserace <- factor(mydata_complete$collapserace)
mydata_complete$collapsepubben <- factor(mydata_complete$collapsepubben)
mydata_complete$collapseeduc <- factor(mydata_complete$collapseeduc)
mydata_complete$employ_collapse <- factor(mydata_complete$employ_collapse)
mydata_complete$collapsezip <- factor(mydata_complete$collapsezip)
mydata_complete$ptsd_bin <- factor(mydata_complete$ptsd_bin)
mydata_complete$phq_bin <- factor(mydata_complete$phq_bin)
mydata_complete$rash_collapse <- factor(mydata_complete$rash_collapse)
mydata_complete$hair_collapse <- factor(mydata_complete$hair_collapse)
mydata_complete$nausea_collapse <- factor(mydata_complete$nausea_collapse)
mydata_complete$irritable_collapse <- factor(mydata_complete$irritable_collapse)
mydata_complete$elevated_collapse <- factor(mydata_complete$elevated_collapse)
mydata_complete$bloodtest_collapse <- factor(mydata_complete$bloodtest_collapse)
mydata_complete$rash_collapse_before <- factor(mydata_complete$rash_collapse_before)
mydata_complete$hair_collapse_before <- factor(mydata_complete$hair_collapse_before)
mydata_complete$nausea_collapse_before <- factor(mydata_complete$nausea_collapse_before)
mydata_complete$irritable_collapse_before <- factor(mydata_complete$irritable_collapse_before)
mydata_complete$bloodtest_collapse_before <- factor(mydata_complete$bloodtest_collapse_before)

imp <- mice(mydata_complete, maxit = 0)

predM <- imp$predictorMatrix
meth <- imp$method

set.seed(123)
imp2 <- mice(mydata_complete, m = 25, print = FALSE)

imp_long <- mice::complete(imp2, action="long", include = TRUE)
imp_long$zip2 <- case_when(
  imp_long$collapsezip=="48502/48503" ~ "48502/48503",
  imp_long$collapsezip=="48504" ~ "48504",
  imp_long$collapsezip=="48505" ~ "48505",
  imp_long$collapsezip=="48506" ~ "48506",
  imp_long$collapsezip=="48507" | imp_long$collapsezip=="48532" ~ "48507/48532"
)

imp_long$collapseeduc2 <- case_when(
  imp_long$collapseeduc=="Less than high school" | imp_long$collapseeduc=="High school" ~ "High school or less",
  imp_long$collapseeduc=="Some college" ~ "Some college",
  imp_long$collapseeduc=="Associate's" | imp_long$collapseeduc=="College degree or more" ~ "Associate's or more"
)

imp_long$zip2 <- with(imp_long, as.factor(imp_long$zip2))
imp_long$collapseeduc2 <- with(imp_long, as.factor(imp_long$collapseeduc2))
imp_long_mids<-as.mids(imp_long)
```

As we know, when trying to understand the effect of a mediated effect on some outcome, we DO NOT adjust for the mediator. However, when trying to understand the effect of the mediator on the outcome, we DO adjust for the mediated effect. Therefore, we have to fit several models for our different outcomes, adjusting for different things depending on what the predictor of interest is. All told, we consider 10 different outcomes (PTSD, PHQ, rashes, hair loss, nausea, irritability, overall number of symptoms, elevated blood lead, getting tested, time to noticing issues) and consider the classes of predictors: demographics/baseline, time to noticing issues/getting tested, elevated blood lead, and emergence of symptoms. This results in us fitting 17 different models, given here:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
effect_estims <- data.frame("Outcome" = NA, "Predictor" = NA, "Estimate" = NA, "SE" = NA, "Pval" = NA)

ptsd_dem <- with(imp_long_mids, glm(ptsd_bin ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2, family="binomial"))

summary(pool(ptsd_dem))

subdat <- data.frame("Outcome" = rep("PTSD", 17), "Predictor" = c("Age", "Male", "Other race", "White", "Receives benefits", "High school or less", "Some college", "Other employment", "Retired", "Unemployed", "Number of children", "Years in Flint", "Network size", "Zip 48504", "Zip 48505", "Zip 48506", "Zip 48507/48532"), "Estimate" = summary(pool(ptsd_dem))[-1,2], "SE" = summary(pool(ptsd_dem))[-1,3], "Pval" = summary(pool(ptsd_dem))[-1,6])

effect_estims <- rbind(effect_estims, subdat)

phq_dem <- with(imp_long_mids, glm(phq_bin ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2, family="binomial"))

summary(pool(phq_dem))

subdat <- data.frame("Outcome" = rep("PHQ", 17), "Predictor" = c("Age", "Male", "Other race", "White", "Receives benefits", "High school or less", "Some college", "Other employment", "Retired", "Unemployed",  "Number of children", "Years in Flint", "Network size", "Zip 48504", "Zip 48505", "Zip 48506", "Zip 48507/48532"), "Estimate" = summary(pool(phq_dem))[-1,2], "SE" = summary(pool(phq_dem))[-1,3], "Pval" = summary(pool(phq_dem))[-1,6])

effect_estims <- rbind(effect_estims, subdat)

rash_dem <- with(imp_long_mids, glm(rash_collapse ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2, family="binomial"))

summary(pool(rash_dem))

subdat <- data.frame("Outcome" = rep("Rashes", 17), "Predictor" = c("Age", "Male", "Other race", "White", "Receives benefits", "High school or less", "Some college", "Other employment", "Retired", "Unemployed", "Number of children", "Years in Flint", "Network size", "Zip 48504", "Zip 48505", "Zip 48506", "Zip 48507/48532"), "Estimate" = summary(pool(rash_dem))[-1,2], "SE" = summary(pool(rash_dem))[-1,3], "Pval" = summary(pool(rash_dem))[-1,6])

effect_estims <- rbind(effect_estims, subdat)

hairloss_dem <- with(imp_long_mids, glm(hair_collapse ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2, family="binomial"))

summary(pool(hairloss_dem))

subdat <- data.frame("Outcome" = rep("Hair loss", 17), "Predictor" = c("Age", "Male", "Other race", "White", "Receives benefits", "High school or less", "Some college", "Other employment", "Retired", "Unemployed", "Number of children", "Years in Flint", "Network size", "Zip 48504", "Zip 48505", "Zip 48506", "Zip 48507/48532"), "Estimate" = summary(pool(hairloss_dem))[-1,2], "SE" = summary(pool(hairloss_dem))[-1,3], "Pval" = summary(pool(hairloss_dem))[-1,6])

effect_estims <- rbind(effect_estims, subdat)

nausea_dem <- with(imp_long_mids, glm(nausea_collapse ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2, family="binomial"))

summary(pool(nausea_dem))

subdat <- data.frame("Outcome" = rep("Nausea", 17), "Predictor" = c("Age", "Male", "Other race", "White", "Receives benefits", "High school or less", "Some college", "Other employment", "Retired", "Unemployed", "Number of children", "Years in Flint", "Network size", "Zip 48504", "Zip 48505", "Zip 48506", "Zip 48507/48532"), "Estimate" = summary(pool(nausea_dem))[-1,2], "SE" = summary(pool(nausea_dem))[-1,3], "Pval" = summary(pool(nausea_dem))[-1,6])

effect_estims <- rbind(effect_estims, subdat)

irritable_dem <- with(imp_long_mids, glm(irritable_collapse ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2, family="binomial"))

summary(pool(irritable_dem))

subdat <- data.frame("Outcome" = rep("Agitation", 17), "Predictor" = c("Age", "Male", "Other race", "White", "Receives benefits", "High school or less", "Some college", "Other employment", "Retired", "Unemployed", "Number of children", "Years in Flint", "Network size", "Zip 48504", "Zip 48505", "Zip 48506", "Zip 48507/48532"), "Estimate" = summary(pool(irritable_dem))[-1,2], "SE" = summary(pool(irritable_dem))[-1,3], "Pval" = summary(pool(irritable_dem))[-1,6])

effect_estims <- rbind(effect_estims, subdat)

overall_dem <- with(imp_long_mids, glm(overall_collapse ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2, family="poisson"))

summary(pool(overall_dem))

subdat <- data.frame("Outcome" = rep("Overall", 17), "Predictor" = c("Age", "Male", "Other race", "White", "Receives benefits", "High school or less", "Some college", "Other employment", "Retired", "Unemployed", "Number of children", "Years in Flint", "Network size", "Zip 48504", "Zip 48505", "Zip 48506", "Zip 48507/48532"), "Estimate" = summary(pool(overall_dem))[-1,2], "SE" = summary(pool(overall_dem))[-1,3], "Pval" = summary(pool(overall_dem))[-1,6])

effect_estims <- rbind(effect_estims, subdat)

#bloodlead_dem <- with(imp_long_mids, logistf(elevated_collapse ~ age + collapsegender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + zip2))

#bloodlead_dem <- lapply(1:5, function(X) logistf(data = select(list_imps[[X]], elevated_collapse, age, collapsegender, collapserace, collapsepubben, number_children, years_cityflint, confidants2, zip2), elevated_collapse ~ age + collapsegender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + zip2, pl = TRUE, dataout = TRUE))

bloodlead_dem <- with(imp_long_mids, glm(elevated_collapse ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2, family = "binomial"))

#test1 <- summary(bloodlead_dem)

#test <- CLIP.confint(obj = bloodlead_dem)
summary(pool(bloodlead_dem))
